Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-10-25 manuscript/supplement.tex
Export mutations by trunk status as a table for manuscript

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/distance-of-simulated-populations-between-timepoints.png}
  \caption{Average weighted distance per year between simulated populations of viruses under the ``naive'' model.}
  \label{sup_fig:distance_of_simulated_populations_between_timepoints}
  \end{center}
\end{figure*}

@@

>>>>

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/distance-of-simulated-populations-between-timepoints.png}
  \caption{
  Average weighted distance per year between simulated populations of viruses under the ``naive'' model.
  \tbc{I'm not sure this figure is worth including.}
  }
  \label{sup_fig:distance_of_simulated_populations_between_timepoints}
  \end{center}
\end{figure*}

@@

\begin{table*}[ht]
  \begin{center}
    \input{tables/mutations_by_trunk_status.tex}
    \caption{
    Number of epitope and non-epitope mutations per branch by trunk or side branch status.
    Epitope sites were defined previously described \cite{Luksza:2014hj}.
    Annotation of trunk and side branch was performed as previously described \cite{Bedford:2015fj}.
    Mutations were calculated for the full validation tree for natural sequences samples between 1990 and 2015.
    }
    \label{sup_table:mutations_by_trunk_status}
  \end{center}
\end{table*}
